Hazardous asteroids forecast via Markov random fields

### 2021-12-09 Presentation/Presentation.tex
PUB

\usepackage[backend=bibtex]{biblatex}
\addbibresource{bibliography.bib}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{Pic/Intro.jpg}}
\title[Hazardous asteroids forecast via Markov random fields]{Hazardous asteroids forecast via Markov random fields}
\subtitle{Project for the exam: Probabilistic Modelling (DSE)}
\author{Marzio De Corato}
\date{\today}

@@

\begin{itemize}
\item \textbf{Final Goal} Assessment of forecasts and interpretability for different machine learning algorithms, including the probabilistic models
\item \textbf{Method} Use a dataset for which the laws that interconnects the different features are known from general principles
\item \textbf{Dataset} CNEOS asteroids dataset for more than 3500 asteroids
\item \textbf{Theoretical laws} Celestial mechanics
\item \textbf{Algorithms involved - probabilistic models} GLASSO, mgm, minforest, mmod
\item \textbf{Algorithms involved - others} Random forest, Support Vector Machines, Quadratic Discriminant Analysis, Logistic Regression

@@

\begin{frame}{Celestial mechanics}
\begin{equation}
\textbf{F}_{1}=\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{1}
\end{equation}

\begin{equation}
\textbf{F}_{2}=-\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{2}
\end{equation}

@@

$\textbf{r} \times \ddot{ \textbf{r}}=0  \implies $ $\textbf{r}$  and $\dot{\textbf{r}}$ lies in the same plane

\begin{frame}{Celestial mechanics}
With polar coordinates  $\hat{\textbf{r}}$ and $\hat{\boldsymbol{\theta}}$

\begin{equation}
\textbf{r}=r\hat{\textbf{r}}
\end{equation}

@@

\begin{frame}{$3^{th}$ Kepler law}

\begin{equation}
\frac{m_{c}+m}{m_{c}+m'}=\left(\frac{a}{a'}\right)\left(\frac{T'}{T}\right)^{2}
\end{equation}

@@

\begin{equation}
(a\a')^{3}\approx (T\T')^{2}
\end{equation}

@@

\begin{center}
The mass of the asteroid is not involve
\end{center}d

@@

\begin{frame}{Orbital parameters}
\begin{center}
\textcolor{red}{Mean motion}
\end{center}
\begin{equation}
n=\frac{2\pi}{T}
\end{equation}

@@

@@

\begin{frame}{Orbital parameters}
\begin{columns}
\column{0.4\textwidth}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth ]{Pic/Mean_anomaly.png}
\caption{\cite{murray1999solar}}
\label{Area_dynamics}
\end{center}
\end{figure}
\column{0.6\textwidth}
\begin{center}
\textcolor{red}{Mean anomaly}
\end{center}
\begin{equation}
M=n(t-\tau)
\end{equation}

@@

\begin{frame}{Orbital parameters}
\begin{columns}
\column{0.4\textwidth}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth ]{Pic/Inclination.png}
\caption{\cite{murray1999solar}}
\label{Area_dynamics}
\end{center}
\end{figure}
\column{0.6\textwidth}
\begin{center}
I: \textcolor{red}{inclination} of the orbit
\end{center}
\begin{center}
$\Omega$: \textcolor{red}{longitude of the ascending node}
\end{center}
\end{columns}
\end{frame}

\begin{frame}{Magnitude}
\begin{equation}
\Phi=\frac{L}{4\pi r^{2}}
\end{equation}
\begin{equation}
m=-2.5\log_{10}\Phi+C
\end{equation}
\begin{equation}
m_{1}-m_{2}=-2.5\log_{10}\frac{\Phi_{1}}{\Phi_{2}}
\end{equation}
\begin{equation}
M-m=-2.5\log_{10}\frac{\Phi\cdot d^{2} }{\Phi\cdot 10^{2}}
\end{equation}
\begin{equation}
M=m+5-5log_{10}d
\end{equation}
Where $\Phi$ is the flux for a sphere of radius r, m the relative magnitude and M the \textcolor{red}{Absolute magnitude}
\end{frame}

\begin{frame}{Magnitude}
\begin{equation}
\Phi=\frac{L}{4\pi r^{2}}
\end{equation}
\begin{equation}
m=-2.5\log_{10}\Phi+C
\end{equation}
\begin{equation}
m_{1}-m_{2}=-2.5\log_{10}\frac{\Phi_{1}}{\Phi_{2}}
\end{equation}
\begin{equation}
M-m=-2.5\log_{10}\frac{\Phi\cdot d^{2} }{\Phi\cdot 10^{2}}
\end{equation}
\begin{equation}
M=m+5-5log_{10}d
\end{equation}
Where $\Phi$ is the flux for a sphere of radius r, m the relative magnitude and M the \textcolor{red}{Absolute magnitude}
\end{frame}

\begin{frame}{Classification}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{Pic/neo_orbit_types.jpg}
\caption{\cite{nasa_classification}}
\label{Area_dynamics}
\end{center}
\end{figure}
\end{frame}

\begin{frame}{Classification}
\begin{itemize}
\item \textbf{Potentially Hazardous Asteroids}: MOID $\leq 0.05$ au $M \leq22.0$ \textit{NEAs whose Minimum Orbit Intersection Distance (MOID) with the Earth is 0.05 au or less and whose absolute magnitude (M) is 22.0 or brighter}
\end{itemize}
\end{frame}

@@

\begin{frame}{Classification}
\begin{itemize}

@@

\begin{frame}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/DENSITY_Perihelion_Distance.pdf}
    \subcaption{ \begin{center}
    a) Perihelion Distance
    \end{center}}
    \vspace{4ex}
  \end{figure} 
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/DENSITY_Eccentricity.pdf}
    \subcaption{ \begin{center}
    b) Eccentricity
    \end{center}}
    \vspace{4ex}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
\begin{columns}

@@

\begin{frame}{FAMD}
\begin{columns}

\column{0.5\textwidth}
    \begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/FAMD.pdf}
\label{FADM}
\end{center}
\end{figure}
  \column{0.5\textwidth}
 \begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/FAMD_Quantitative variables.pdf}
\label{FAMD_Quantitative variables}
\end{center}
\end{figure}
\end{columns}
\end{frame}

\begin{frame}{Mutual information}
\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{Pic/Mutual_information.pdf}
\label{Mutual_information}
\end{center}
\end{figure}
\end{frame}

\section{Prob. models}

\begin{frame}{GLASSO}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.1.pdf}
    \subcaption{$\rho$=0.2 \begin{center}
    \end{center}}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.2.pdf}
    \subcaption{$\rho$=0.2 \begin{center}
    \end{center}}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}{GLASSO}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.3.pdf}
    \subcaption{$\rho$=0.3 \begin{center}
    \end{center}}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.4.pdf}
    \subcaption{$\rho$=0.4 \begin{center}
    \end{center}}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}{Mixed interactions: mgm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/mgm.pdf}
\label{mgm}
\end{center}
\end{figure}
\end{frame}

\begin{frame}{Mixed interactions: minforest}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/minforest.pdf}
\label{mgm}
\end{center}
\end{figure}
\end{frame}

\begin{frame}{Mixed interactions: mmod}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/mmod.pdf}
\label{mgm}
\end{center}
\end{figure}
\end{frame}

@@

\section{Other ML alg.}
\begin{frame}{Random Forest}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/RF_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_RF.pdf}
  \end{figure}
\end{columns}
\end{frame}

@@

\begin{frame}{Support Vector Machines}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/SVM_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_SVM.pdf}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}{Quadratic Discriminant Analysis (QDA)}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/QDA_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_QDA.pdf}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}{Logistic regression}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/Logisic_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_Logistic.pdf}
  \end{figure}
\end{columns}
\end{frame}

@@

@@

\begin{equation}
\begin{split}
P(X)= & \exp \left\lbrace \sum_{s\in V}\theta_{s}\phi_{s}(X_{s})+\sum_{s\in V}\sum_{r\in N(s)}\theta_{s,r}\phi_{s}(X_{s})\phi_{r}(X_{r})+...+\\&\sum_{r_{1},...,r_{k}\in C}\theta_{r1,...,rk}\prod_{j=1}^{k}\phi_{r}_{j}\left(X_{r}_{j}\right)+\sum_{s\in V}B_{s}(X_{S})-\Phi(\theta) \right\rbrace
\end{split}
\end{equation}

@@

\begin{frame}{Ref}
\printbibliography
\end{frame}

>>>>

\usepackage[backend=bibtex]{biblatex}
\addbibresource{bibliography.bib}
\newtheorem*{remark}{Remark}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{Pic/Intro.jpg}}
\title[Hazardous asteroids forecast via Markov random fields]{Hazardous asteroids forecast via Markov random fields}
\subtitle{Project for the exam: Probabilistic Modelling (DSE)}
\author{Marzio De Corato}
\date{\today}

@@

\begin{itemize}
\item \textbf{Final Goal} Assessment of forecasts and interpretability for different machine learning algorithms, including the probabilistic models
\item \textbf{Method} Use a dataset for which the laws that interconnect the different features are known from general principles
\item \textbf{Dataset} CNEOS asteroids dataset for more than 3500 asteroids
\item \textbf{Theoretical laws} Celestial mechanics
\item \textbf{Algorithms involved - probabilistic models} GLASSO, mgm, minforest, mmod
\item \textbf{Algorithms involved - others} Random forest, Support Vector Machines, Quadratic Discriminant Analysis, Logistic Regression

@@

\begin{frame}{Celestial mechanics \cite{murray1999solar}: equations of motion}

\begin{center}
Lets Consider the interaction between a planet of mass $m_{1}$ at the  position $r_{1}$ (inertial frame) and an asteroid of mass $m_{2}$  at the position $r_{2}$
\end{center}

\begin{equation}
\textbf{F}_{1}=\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{1}\quad \textbf{F}_{2}=-\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{2}
\end{equation}

@@

\begin{center}
$\textbf{r} \times \ddot{ \textbf{r}}=0  \implies $ $\textbf{r}$  and $\dot{\textbf{r}}$ lies in the same plane

\end{center}
\end{frame}

\begin{frame}{Celestial mechanics \cite{murray1999solar}: equations of motion}
\begin{center}
With polar coordinates  $\hat{\textbf{r}}$ and $\hat{\boldsymbol{\theta}}$
\end{center}
\begin{equation}
\textbf{r}=r\hat{\textbf{r}}
\end{equation}

@@

\begin{frame}{Celestial mechanics \cite{murray1999solar}: $3^{th}$ Kepler law}

\begin{equation}
\frac{m_{c}+m}{m_{c}+m'}=\left(\frac{a}{a'}\right)^{3}\left(\frac{T'}{T}\right)^{2}
\end{equation}

@@

\begin{equation}
\left(\frac{a}{a'}\right)^{3}\approx \left(\frac{T}{T'}'\right)^{2}
\end{equation}

@@

\begin{center}
\textbf{Remark:} The mass of the asteroid is \textbf{not} involved
\end{center}

@@

\begin{frame}{Celestial mechanics \cite{murray1999solar}: Orbital parameters}
\begin{center}
\textcolor{red}{Mean motion} $n=\frac{2\pi}{T}$
\end{center}

@@

\begin{center}
\textbf{Remark:} The mean motion of an asteroid is different with respect to the the asteroid relative velocity (measured from Earth), since the latter is different at the perihelion an at the aphelion
\end{center}

@@

\begin{frame}{Celestial mechanics \cite{murray1999solar}: Orbital parameters}
\begin{columns}
\column{0.4\textwidth}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth ]{Pic/Mean_anomaly.png}
\caption{\cite{murray1999solar}}
\label{Area_dynamics}
\end{center}
\end{figure}
\column{0.6\textwidth}
\begin{center}
\textcolor{red}{Mean anomaly}
\end{center}
\begin{equation}
M=n(t-\tau)
\end{equation}

@@

\begin{frame}{Celestial mechanics \cite{murray1999solar}: Orbital parameters}

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth ]{Pic/Inclination.png}
\caption{\cite{murray1999solar}}
\label{Area_dynamics}
\end{center}
\end{figure}

\begin{center}
I: \textcolor{red}{inclination} of the orbit
\end{center}
\begin{center}
$\Omega$: \textcolor{red}{longitude of the ascending node}
\end{center}
\end{frame}

\begin{frame}{Celestial mechanics \cite{murray1999solar}: Magnitude}
\begin{equation}
\Phi=\frac{L}{4\pi r^{2}}
\end{equation}
\begin{equation}
m=-2.5\log_{10}\Phi+C
\end{equation}
\begin{equation}
m_{1}-m_{2}=-2.5\log_{10}\frac{\Phi_{1}}{\Phi_{2}}
\end{equation}
\begin{equation}
M-m=-2.5\log_{10}\frac{\Phi\cdot d^{2} }{\Phi\cdot 10^{2}}
\end{equation}
\begin{equation}
M=m+5-5log_{10}d
\end{equation}
Where $\Phi$ is the flux for a sphere of radius r, m the relative magnitude and M the \textcolor{red}{Absolute magnitude}
\end{frame}

\begin{frame}{Celestial mechanics \cite{murray1999solar}: Magnitude}
\begin{equation}
\Phi=\frac{L}{4\pi r^{2}}
\end{equation}
\begin{equation}
m=-2.5\log_{10}\Phi+C
\end{equation}
\begin{equation}
m_{1}-m_{2}=-2.5\log_{10}\frac{\Phi_{1}}{\Phi_{2}}
\end{equation}
\begin{equation}
M-m=-2.5\log_{10}\frac{\Phi\cdot d^{2} }{\Phi\cdot 10^{2}}
\end{equation}
\begin{equation}
M=m+5-5log_{10}d
\end{equation}
Where $\Phi$ is the flux for a sphere of radius r, m the relative magnitude and M the \textcolor{red}{Absolute magnitude}
\end{frame}

\begin{frame}{Celestial mechanics \cite{nasa_classification}: Classification}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{Pic/neo_orbit_types.jpg}
\caption{\cite{nasa_classification}}
\label{Area_dynamics}
\end{center}
\end{figure}
\end{frame}

\begin{frame}{Celestial mechanics \cite{nasa_classification}: Classification}
\begin{itemize}
\item \textbf{Potentially Hazardous Asteroids}: MOID $\leq 0.05$ au $M \leq22.0$ \textit{NEAs whose Minimum Orbit Intersection Distance (MOID) with the Earth is 0.05 au or less and whose absolute magnitude (M) is 22.0 or brighter}
\end{itemize}
\end{frame}

@@

\begin{frame}{Dataset}
\begin{itemize}

@@

\begin{frame}{Density Plot}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/DENSITY_Perihelion_Distance.pdf}
    \subcaption{ \begin{center}
    a) Perihelion Distance
    \end{center}}
    \vspace{4ex}
  \end{figure} 
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/DENSITY_Eccentricity.pdf}
    \subcaption{ \begin{center}
    b) Eccentricity
    \end{center}}
    \vspace{4ex}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}{Density Plot}
\begin{columns}

@@

\begin{frame}{FAMD }
\begin{columns}

\column{0.5\textwidth}
    \begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/FAMD.pdf}
\label{FADM}
\end{center}
\end{figure}
  \column{0.5\textwidth}
 \begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/FAMD_Quantitative variables.pdf}
\label{FAMD_Quantitative variables}
\end{center}
\end{figure}
\end{columns}
\begin{center}
Performed with the FactoMineR package \cite{le2008factominer} 
\end{center}
\end{frame}

\begin{frame}{Mutual information analysis}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Pic/Mutual_information.pdf}
\label{Mutual_information}
\end{center}
\end{figure}
\begin{center}
Performed with the varrank package \cite{kratzer2018varrank} 
\end{center}
\end{frame}

\section{Prob. mod.}

\begin{frame}{GLASSO}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.1.pdf}
    \subcaption{$\rho$=0.2 \begin{center}
    \end{center}}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.2.pdf}
    \subcaption{$\rho$=0.2 \begin{center}
    \end{center}}
  \end{figure}
\end{columns}
\begin{center}
Performed with the GLASSO package \cite{glasso}
\end{center}
\end{frame}

\begin{frame}{GLASSO}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.3.pdf}
    \subcaption{$\rho$=0.3 \begin{center}
    \end{center}}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Pic/GLASSO_0.4.pdf}
    \subcaption{$\rho$=0.4 \begin{center}
    \end{center}}
  \end{figure}
\end{columns}
\begin{center}
Performed with the GLASSO package \cite{glasso}
\end{center}
\end{frame}

\begin{frame}{Mixed interactions: mgm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/mgm.pdf}
\label{mgm}
\end{center}
\end{figure}
\begin{center}
Performed with the mgm package \cite{haslbeck2015mgm}
\end{center}
\end{frame}

\begin{frame}{Mixed interactions: minforest}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/minforest.pdf}
\label{mgm}
\end{center}
\end{figure}
\begin{center}
Performed with the gRapHD package \cite{de2009high}
\end{center}
\end{frame}

\begin{frame}{Mixed interactions: mmod}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{Pic/mmod.pdf}
\label{mgm}
\end{center}
\end{figure}
\begin{center}
Performed with the gRim package \cite{grim}
\end{center}
\end{frame}

@@

\section{Other ML alg.}
\begin{frame}{Random Forest}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/RF_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_RF.pdf}
  \end{figure}
\end{columns}
\begin{center}
Performed with the rfor package \cite{rfor}
\end{center}
\end{frame}

@@

\begin{frame}{Support Vector Machines}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/SVM_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_SVM.pdf}
  \end{figure}
\end{columns}
\begin{center}
Performed with the e1071 package \cite{dimitriadou2008misc}
\end{center}
\end{frame}

\begin{frame}{Quadratic Discriminant Analysis (QDA)}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/QDA_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_QDA.pdf}
  \end{figure}
\end{columns}
\begin{center}
Performed with the MASS package \cite{MASS}
\end{center}
\end{frame}

\begin{frame}{Logistic regression}
\begin{columns}
\column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/Logisic_confusion.pdf}
  \end{figure} 
  \column{0.5\textwidth}
  \begin{figure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{Pic/ROC_Logistic.pdf}
  \end{figure}
\end{columns}
\begin{center}
Performed with the stats package \cite{stats}
\end{center}
\end{frame}

@@

\begin{frame}{Interpretability and scientific validation}

\begin{remark}[Interpretability - Tarski definition]
The formal theory T can be translated into S if and only if S can prove the theorem of T in its language \cite{tarski1953undecidable}
\end{remark}

\begin{frame}{Interpretability and scientific validation}

\begin{remark}[Scientific method - Einstein definition]
Science uses the totality of the primary concepts, i.e., concepts directly connected with sense experiences, and propositions connecting them. Such a state of affairs cannot, however, satisfy a spirit which is really scientifically minded; because the totality of concepts and relations obtained in this manner is utterly lacking in logical unity. In order to supplement this deficiency, one invents a system poorer in concepts and relations, a system retaining the primary concepts and relations of the \textit{first layer} as logically derived concepts and relations. This new \textit{secondary system} pays for its higher logical unity by having elementary concepts (concepts of the second layer), which are no longer directly connected with complexes of sense experiences \cite{physics-reality}
\end{remark}

\begin{frame}{Interpretability and scientific validation}

\begin{remark}[Scientific method - Einstein definition ]
The essential thing is the aim to represent the multitude of concepts and propositions, close to experience, as propositions, logically deduced from a basis, as narrow as possible, of fundamental concepts and fundamental relations which themselves can be chosen freely (axioms) \cite{physics-reality}
\end{remark}

@@

\begin{equation}
\begin{split}
P(X)= & \exp \left( \sum_{s\in V}\theta_{s}\phi_{s}(X_{s})+\sum_{s\in V}\sum_{r\in N(s)}\theta_{s,r}\phi_{s}(X_{s})\phi_{r}(X_{r})\\ +&...+\sum_{r_{1},...,r_{k}\in C}\theta_{r1,...,rk}\prod_{j=1}^{k}\phi_{r}_{j}\left(X_{r}_{j}\right)+\sum_{s\in V}B_{s}(X_{S})-\Phi(\theta) \right)
\end{split}
\end{equation}

@@

\begin{frame}[t,allowframebreaks]
\frametitle{Bibliography}
\printbibliography
\end{frame}
